PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-23 paper.tex
Update on Overleaf.
Added the list of recorded streams

\usepackage{natbib}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

@@

@@

\section{Dataset Structure}

>>>>

\usepackage{natbib}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{booktabs}

@@

\todo[inline]{mention robot greetings: expectation that the robot can talk
(and likely, hear)}
\todo[inline]{mention idea box}
\todo[inline]{mention robot calibration phase (between 0 and }

@@

\section{The PInSoRo Dataset}

\subsection{Structure}

The dataset consists in a collection of records. Each record correspond to one
play interaction between two children. To date (June 2017) \todo[inline]{put
latest nb} records have been acquired. At the end of the acquisition campaign
(July 2017), the dataset is planned to include 50 records (\ie 100 children). As
mentioned above, the duration of each play episode varies ($M=17m13s,
SD=8m02s$), but it is capped to a maximum of 40 minutes.

\begin{table}[]
\centering
\caption{List of datastreams stored in each record}
\label{table|datastreams}
\begin{tabular}{@{}lll@{}}
\toprule
\bf Domain  & \bf Type                              & \bf Details                              \\ \midrule
child 1     & audio                                 & 16kHz, mono, semi-directional        \\
            & face (RGB)                            & qHD (960$\times$540), 30Hz           \\
            & face (depth)                          & VGA (640$\times$480), 30Hz           \\
            & facial features                       & 68 3D points (point cloud)           \\ \midrule
child 2     & audio                                 & 16kHz, mono, semi-directional        \\
            & face (RGB)                            & qHD (960$\times$540), 30Hz           \\
            & face (depth)                          & VGA (640$\times$480), 30Hz           \\
            & facial features                       & 68 3D points (point cloud)           \\ \midrule
environment & RGB                                   & qHD (960$\times$540), 29.7Hz         \\ \midrule
touchscreen & background drawing (RGB)              & 4Hz                                  \\
            & touches                               & 6 points multi-touch                 \\
            & items position and orientation        &                                      \\ \midrule
others      & \multicolumn{2}{l}{annotations of social behaviours and remarkable events}   \\
            & \multicolumn{2}{l}{static transforms between touchscreen and facial cameras} \\
            & \multicolumn{2}{l}{cameras calibration informations}                         \\ \bottomrule
\end{tabular}
\end{table}
